Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Dramatically Increases Repair Time?

### 2015-02-23 phaseDelay.tex
various things

\begin{figure}
\begin{center}
\scriptsize
\begin{tabular}{rrl}
year& \# issues&\\\hline
2006 &  44 &\\
2007 &  34 &\\
2008&  288 &\rule{1mm}{2mm}\\
2009&  846 &\rule{3mm}{2mm}\\
2010& 1007 &\rule{3mm}{2mm}\\
2011& 3273 &\rule{10mm}{2mm}\\
2012&18102 &\rule{45mm}{2mm}\\
2013&20336 &\rule{50mm}{2mm}\\
2014& 3307 & \rule{10mm}{2mm}\\\cline{1-2}
Total:&47228
\end{tabular}
\end{center}
\caption{This paper studies 47,228 issues recorded 2006 to 2014.}\label{fig:years}
\end{figure}
\begin{figure*}[!t]
\begin{center}
\includegraphics[width=6in]{waterfall2.png}
\end{center}
\caption{Different approaches to software development:  waterfall and agile (bottom left).}
\end{figure*}

@@

\renewcommand{\baselinestretch}{0.7}
\small
\begin{center}
\begin{tabular}{ll|r|rl}
            &                  & Sample\\
Phase injected & Phase removed & size & \multicolumn{2}{l}{Scale up, w.r.t. to first phase}
\input{deltas}
\end{tabular}
\end{center}
\caption{Scale ups for median time to resolve issues (taken from \fig{raw}).}
\label{fig:scale}
\end{figure*}

@@

A common property of real-world data sets is the presence
of noisy entries (superfluous  or spurious data). 
The level of noise can be quite high. As reported
in \cite{shepperd12}, around
10\% to 30\%
of the records in the NASA MDP defect data sets are
affected by noise. Nichols et al.~\cite{shirai14}  report that
the noise levesl in the SEI TSE data are smaller than those seen
in other data sets. They found in the SEI TSP data that:\bi 
\item
4\% of the data was incorrect such as  null values of illegal formats;
\item  2\% of the data has inconsistencies such as timestamps
where the stop time was before the start time;
\item 3\% of the data had data that was not credible
such as tasks listed in one day that took like than six hours.
\ei 
That said, certain semantic features of the SEI TSP data should be noted.
Firstly, in the current TSP collection tool, 
fix times are only the developer time for the developer walking through the phased of \fig{waterfall}.
We are currently tracking the fix time for later issues (e.g. those raised during  acceptance test and later
product life cycle). Informally, we can say that in that data we have not detected
a dramatic phase escalation effect (but we have nothing definitive yet to publish  at this time).

@@

The defect typ that we studied were
\be 
\item design, compile, test, or other support system problems = Environment
procedure calls and reference, I/O, user formats = Interface
structure, content = Data
comments, messages = Documentation
spelling, punctuatio typos, instruction formats = Syntax
logic, pointers, loops, recursion, computation, function defects = Function
error messages, inadequate checks = Checking
change management, library, version control = Build, package
declaration, duplicate names, scope, limits = Assignment
configuration, timing, memory = System
\section{Conclusion}

>>>>

\begin{figure}
\begin{center}
\begin{tabular}{rrl}
year& \# issues&\\\hline
2006 &  44 &\\
2007 &  34 &\\
2008&  288 &\rule{1mm}{2mm}\\
2009&  846 &\rule{3mm}{2mm}\\
2010& 1007 &\rule{3mm}{2mm}\\
2011& 3273 &\rule{10mm}{2mm}\\
2012&18102 &\rule{45mm}{2mm}\\
2013&20336 &\rule{50mm}{2mm}\\
2014& 3307 & \rule{10mm}{2mm}\\\cline{1-2}
Total:&47228
\end{tabular}
\end{center}
\caption{This paper studies 47,228 issues recorded 2006 to 2014.}\label{fig:years}
\end{figure}
\begin{figure*}[!t]
\begin{center}
\includegraphics[width=6in]{waterfall2.png}
\end{center}
\caption{Different approaches to software development:  waterfall and agile (bottom left).}
\end{figure*}

@@

\renewcommand{\baselinestretch}{0.7} 
\begin{center}
\begin{tabular}{ll|r|rl}
            &                  & Sample\\
Phase injected & Phase removed & size & \multicolumn{2}{l}{Scale up, w.r.t. to first phase}
\input{deltas}
\end{tabular}
\end{center}
\caption{50th percentile (median) scale ups  for  time to resolve issues (taken from \fig{raw}).}
\label{fig:scale}
\end{figure*}

In these results, we checked if a small number of bugs are most expensive. 
To check this:
\bi
\item
We repeated the analysis that generated \fig{scale},
but instead of looking at the 50th percentile, we displayed the scale up factors
\item 
We only
checked the Design and Code scale up results since, from \fig{scale}, it is clear these
have the most examples of longest phase delays.
\ei 
The  results are shown in \fig{scale90} and these
results are somewhat different for Design and Coding issues:
\bi 
\item For Design issues,  these have the same
general form as the 50th percentile results. That is, while it it certainly faster
to remove thing sin the phase where they are created, once we leave that phase
it does not seem to matter much how many phases we wait before fixing the issue.
\begin{itemize}
\item For Coding issues, the seems little impact of phase delay on the time
required to fix.
\end{itemize}

\renewcommand{\baselinestretch}{0.7} 
\begin{center}
\begin{tabular}{ll|r|rl}
            &                  & Sample\\
Phase injected & Phase removed & size & \multicolumn{2}{l}{Scale up, w.r.t. to first phase}
\input{deltaBig}
\end{tabular}
\end{center}
\caption{90th percentile scale ups  for  time to resolve issues .}
\label{fig:scale90}
\end{figure*}

@@

A common property of real-world data sets is the presence
of noisy entries (superfluous  or spurious data). 
The level of noise can be quite high. As reported
in \cite{shepperd12}, around
10\% to 30\%
of the records in the NASA MDP defect data sets are
affected by noise. Nichols et al.~\cite{shirai14}  report that
the noise levesl in the SEI TSE data are smaller than those seen
in other data sets. They found in the SEI TSP data that:\bi 
\item
4\% of the data was incorrect such as  null values of illegal formats;
\item  2\% of the data has inconsistencies such as timestamps
where the stop time was before the start time;
\item 3\% of the data had data that was not credible
such as tasks listed in one day that took like than six hours.
\ei 
That said, certain semantic features of the SEI TSP data should be noted.
Firstly, in the current TSP collection tool, 
fix times are only the developer time for the developer walking through the phases of \fig{waterfall}.
We are currently tracking the fix time for post-release issues (e.g. those raised during  acceptance test and later
product life cycle). So far, in that post-release data,  we have not detected
a dramatic phase escalation effect (but at this time, we have nothing definitive comment on that matter).

@@

The defect typ that we studied were
\be 
\item design, compile, test, or other support system problems = Environment
procedure calls and reference, I/O, user formats = Interface
structure, content = Data
comments, messages = Documentation
spelling, punctuatio typos, instruction formats = Syntax
logic, pointers, loops, recursion, computation, function defects = Function
error messages, inadequate checks = Checking
change management, library, version control = Build, package
declaration, duplicate names, scope, limits = Assignment
configuration, timing, memory = System
\ee
\section{Conclusion}
